Open Preprints in Ecology \& Evolution

### 2012-09-07 ms.tex
Added section on cultural barriers to adoption of preprint servers

>>>>

There are other ``cultural'' barriers to adoption of preprint servers
by ecologists and evolutionary biologists.  The most notable preprint
server, arXiv, is designed to work best with \TeX{}, a nearly
universal document preparation system among physicists and
mathematicians.  Jackson \cite{jackson2002preprints} further argues
that \TeX{} introduced an ``open source mindset'' to its users, who
now freely share their research findings as well as their software.
Many biologists instead use proprietary software to prepare their
research findings, and many ecology and evolution journals officially
prefer Microsoft Word documents as submissions.  The recent
discipline-wide adoption of free software packages such as R, as well
as interest in open access publishing, has coincided with recent use
of preprint servers by biologists, supporting Jackson's claims.
